ramipril cough amlodipine (by ArticleAggregator_v05)

### 2023-02-21 ArticleAggregatorCS.qmd
Results for tadalafil continous ready in egp.xlsx
ramipril cough amlodipine

---
title: "continuous tadalafil (by ArticleAggregator_v05)"
author: "ReCodeRa"
format: html
server: shiny
editor: 
  markdown: 
    wrap: 72
---

@@

@@

```{r}
#| label: Environment Setup
final_col_names <- c("Title", "Author", "Year", "FTlink", "Src", "Info", "PubDate", "PubType", "Abstract", "CT", "PMID", "PUI", "DOI", "EBlink", "OpenLink") 
term <- "continuous tadalafil"
aa_path <- "/workspaces/WebScrap/ArticleAggregator_data/"
setwd(aa_path)
```

@@

# write_xlsx(eb, glue("{aa_path}eb_to_merge.xlsx"))
# Correct for Van Der Lee manually

@@

# write_xlsx(gs, glue("{aa_path}gs_to_merge.xlsx"))

>>>>

---
title: "ramipril cough amlodipine (by ArticleAggregator_v05)"
author: "ReCodeRa"
format: html
server: shiny
editor: 
  markdown: 
    wrap: 72
---

@@

## Procedure
- EMBASE search: search in ""

@@

```{r}
#| label: Environment Setup
final_col_names <- c("Title", "Author", "Year", "FTlink", "Src", "Info", "PubDate", "PubType", "Abstract", "CT", "PMID", "PUI", "DOI", "EBlink", "OpenLink") 
term <- "ramipril cough amlodipine"
aa_path <- "/workspaces/WebScrap/ArticleAggregator_data/rami/"
setwd(aa_path)
```

@@

write_xlsx(eb, glue("{aa_path}eb_to_merge.xlsx"))
# Correct for Van Der Lee manually

@@

write_xlsx(gs, glue("{aa_path}gs_to_merge.xlsx"))
